Near Optimal Behavior with Approximate Abstraction

### 2016-02-04 paper/example_domains.tex
trimmed code para'

%Description of code base
Additionally, in hopes of promoting further investigation into approximate abstraction, we provide our code base (link redacted for review) which provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}. We use the graph visualization library GraphStream~\cite{graphstream} and planning and \ac{RL} library, BURLAP~\cite{BURLAPCITATION}.

>>>>

%Description of code base
Our code base (link redacted for review) provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}. We use the graph visualization library GraphStream~\cite{graphstream} and planning and \ac{RL} library, BURLAP~\cite{BURLAPCITATION}.
